\documentclass[letterpaper,10pt]{article}
\usepackage[default]{opensans}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{adjustbox}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{textcomp}
\usepackage{silence}
\WarningFilter{latex}{Command \showhyphens has changed}

\linespread{1.1}
\textheight=10in
\pagestyle{empty}
\setlist[itemize]{nosep, itemsep=1pt, leftmargin=*}
\raggedright
\usepackage[left=0.6in,right=0.6in,bottom=0.4in,top=0.6in]{geometry}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\newcommand{\header} [1] {
  {\hspace*{-18pt}\vspace*{5pt} #1}
  \vspace*{-3pt} \hrulefill \\ \vspace*{5pt}
}

\begin{document}
\begin{sloppypar}
  \vspace*{-30pt}
  \sloppy
  \setlength{\emergencystretch}{5em}

  \begin{center}
    {\Huge Tahmidul Islam} \\
    me@tahmidul612.com $\cdot$ (437)-223-0422 $\cdot$ \href{https://tahmidul612.com}{tahmidul612.com} $\cdot$ \href{https://www.linkedin.com/in/tahmidul612}{linkedin.com/in/tahmidul612} \\
  \end{center}

  \header{Education}
  \textbf{Lakehead University}\hfill Thunder Bay, Ontario\\
  HBSc Computer Science \hfill January 2019 - May 2024\\
  \vspace{1.5mm}

  \header{Work Experience}
  \textbf{Raphael Stone USA} \hfill Remote\\
  \textit{Freelance Automation Developer} \hfill Jun 2018 - July 2018\\
  \vspace{1.5mm}
  \begin{itemize}
    \item Developed Google Apps Script automation for parsing and importing email data into Google Sheets.
    \item Implemented Zapier automation with Twilio integration to streamline workflows.
  \end{itemize}
  \vspace{1.5mm}
  \textbf{AI Buddy Catalyst Labs} \hfill Remote\\
  \textit{Automation Development Intern} \hfill May 2025 - Current\\
  \vspace{1.5mm}
  \begin{itemize}
    \item Built AI agents and automation pipelines in n8n.
    \item Wrote Ansible scripts and CD workflows in Github Actions for deployment automation.
  \end{itemize}
  \vspace{1.5mm}

  \header{Skills}
  \textbf{Programming Languages:} Python, Java, C++, JavaScript, Bash, Powershell \\
  \textbf{Tools and Frameworks:} n8n, Flask, Git, Docker, Zapier, GameCI, CI/CD with Github Actions \\
  \textbf{Cloud Platforms:} Google Cloud Platform (GCP), AWS (EC2, S3) \\
  \textbf{Server Management:} Ubuntu Server, Hyper-V, Docker Swarm, Portainer, Ansible, Homelab (5 years) \\
  \textbf{Operating Systems:} Windows 7/8/10/11, MacOS, Debian distros, Arch distros

  \header{Projects}
  \textbf{Full-Stack AI-Powered URL Shortener} {\sl Python, Flask, AWS EC2, Django, NLP, GitHub Actions} \\
  Developed an AI-powered URL shortening service using Flask and Django. Integrated a pre-trained RoBERTa model to generate relevant slugs, enhancing user experience. Deployed on AWS EC2, automating updates and scaling using GitHub Actions.

  \textbf{Cloud-Based Game Development Workflow} {\sl Unity, C\#, GameCI, GitHub Actions, GitHub Pages} \\
  Built and deployed two games using Unity and HaxeFlixel, implementing game mechanics in C\# and Haxe. Leveraged GameCI for automated builds and deployments. Used GitHub Actions for CI/CD and deployed the final game to GitHub Pages.

  \textbf{Automated Calendar Data Importer} {\sl Python, Google App Script, Web Scraping, CI/CD} \\
  Created a Python script to automate calendar updates for free concerts in Toronto. Utilized web scraping to parse schedule data and generate ICS files. Implemented Google Apps Script integration for automatic synchronization with Google Calendar.

  \vspace{1.5mm}
  \header{Awards}
  \begin{tabular}{@{}p{0.78\textwidth}p{0.19\textwidth}@{}}
    \textbf{Dean's List} & Lakehead University \\
    Recognized for excellent academic performance in the 2020-21 academic year. & 2021 \\
    \textbf{Level 3 of Lakehead Makes Leaders} & Lakehead University \\
    Won the "Think Like a Boss" module, competing in a simulated investment portfolio challenge. & November 2021 \\
  \end{tabular}

  \vspace{1.5mm}
  \header{References}
  \begin{tabular}{@{}p{0.48\textwidth}p{0.48\textwidth}@{}}
    % Left Column - Sadab Seraj
    \textbf{Sadab Seraj} &
    % Right Column - Aukik Aurnab
    \textbf{Aukik Aurnab} \\

    Project Manager &
    Chief Technology Officer \\

    Raphael Porcelain, USA &
    AI Buddy Catalyst Labs, Bismo and Katerout \\

    Email: \href{mailto:justsadab@gmail.com}{\texttt{justsadab@gmail.com}} &
    Email: \href{mailto:aukikaurnabx@gmail.com}{\texttt{aukikaurnabx@gmail.com}} \\

    Worked closely on implementing &
    Phone: \texttt{+880-168-007-7890} \\

    automation pipelines. &
    Linkedin: \href{https://www.linkedin.com/in/aukik-aurnab/}{\texttt{linkedin.com/in/aukik-aurnab/}} \\
  \end{tabular}

\end{sloppypar}
\end{document}